A Multi-Modal Model of Object Deformation under Robotic Pushing

### 2016-12-26 twostagedo-rev-Dec-16.tex
Fixed missing reference to figure.

\comment{We also compared the generalisation capabilities of our model against the system proposed in \cite{Cretu2012}.  This system uses a Growing Neural Gas (GNG) Network to calibrate a colour segmentation algorithm.  We couldn't use the HSV space, as suggested by Cretu, because our videos have lots of shadows which produce holes inside the material regions which cause problems in further stages.  We obtained better results for GNGN with the Luv color space.  Note that, even though we used the HSV space in our tracking algorithm, this didn't have the same problems because the nodes of our linear snake search for nearby edges and are not affected by shadows in the middle of the object or temporary failures in detecting an edge.  Another GNG network is used to select the control points adequate for approximating the contour in the first frame.  Later, Cretu et al. used a Neural Gas (NG) algorithm to adjust that fixed number of control points to the contour of the material at every frame.  Using the coordinates of the finger, the sensed force and the coordinates of those control points through time, they train a Feedforward Neural Network (FFNN) to predict the contour of the material given the position of the finger and sensed force.  We reproduced those steps and their training method on our training video.  However, when we tried to test the generalisation capabilities of their method to new pushing actions, the weakness of the FFNN method became evident: it became tied to the specific location and type of interaction it was trained with, while our physics based model had no problem making predictions for new pushing actions.  The results with the GNGN method can be seen in \fref{fig:cretu_prediction}.

@@

\begin{figure}[!t]
\centering
\includegraphics[width=3.5in]{sponge__result.jpg}
\caption{Neural network approach fits quite well the training data set, but can not generalise to new pushing actions.  The red line shows the border used as ground truth in the training set, while yellow lines show prediction from the FFNN.}\label{fig:cretu_prediction}
\end{figure}
\begin{figure}[!t]
\centering
\includegraphics[width=3.5in]{plasticine__result.jpg}
\caption{GNG segmentation didn't work with a shadowed material (video of plasticine). This image shows the segmentation results previous to the application the median filter, which was applied to perform tracking.  Results also do not generalise to unseen pushing actions.  The red line shows the border used as ground truth in the training set, while yellow lines show prediction from the FFNN.}\label{fig:cretu_prediction}
\end{figure}

>>>>

\comment{We also compared the generalisation capabilities of our model against the system proposed in \cite{Cretu2012}.  This system uses a Growing Neural Gas (GNG) Network to calibrate a colour segmentation algorithm.  We couldn't use the HSV space, as suggested by Cretu, because our videos have lots of shadows which produce holes inside the material regions which cause problems in further stages.  We obtained better results for GNGN with the Luv color space.  Note that, even though we used the HSV space in our tracking algorithm, this didn't have the same problems because the nodes of our linear snake search for nearby edges and are not affected by shadows in the middle of the object or temporary failures in detecting an edge.  Another GNG network is used to select the control points adequate for approximating the contour in the first frame.  Later, Cretu et al. used a Neural Gas (NG) algorithm to adjust that fixed number of control points to the contour of the material at every frame.  Using the coordinates of the finger, the sensed force and the coordinates of those control points through time, they train a Feedforward Neural Network (FFNN) to predict the contour of the material given the position of the finger and sensed force.  We reproduced those steps and their training method on our training video.  However, when we tried to test the generalisation capabilities of their method to new pushing actions, the weakness of the FFNN method became evident: it became tied to the specific location and type of interaction it was trained with, while our physics based model had no problem making predictions for new pushing actions.  The results with the GNGN method can be seen in \fref{fig:cretu_prediction_sponge} and \fref{fig:cretu_prediction_plasticine}.

@@

\begin{figure}[!t]
\centering
\includegraphics[width=3.5in]{sponge__result.jpg}
\caption{Neural network approach fits quite well the training data set, but can not generalise to new pushing actions.  The red line shows the border used as ground truth in the training set, while yellow lines show prediction from the FFNN.}\label{fig:cretu_prediction_sponge}
\end{figure}
\begin{figure}[!t]
\centering
\includegraphics[width=3.5in]{plasticine__result.jpg}
\caption{GNG segmentation didn't work with a shadowed material (video of plasticine). This image shows the segmentation results previous to the application the median filter, which was applied to perform tracking.  Results also do not generalise to unseen pushing actions.  The red line shows the border used as ground truth in the training set, while yellow lines show prediction from the FFNN.}\label{fig:cretu_prediction_plasticine}
\end{figure}
